---
title: "Code and Data for: BEA papers"
author:
  - Lars Vilhuber
date: "`r Sys.Date()`"
output:
  html_document: 
    keep_md: yes
    number_sections: yes
    toc: yes
    toc_depth: 1
  word_document: default
  pdf_document: 
    toc: true
    number_sections: true
    toc_depth: 1
editor_options: 
  chunk_output_type: console
---



```{r setup,echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval=TRUE)

source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=FALSE)

we.are.README <- TRUE

source(file.path(basepath,"global-libraries.R"),echo=FALSE)
source(file.path(programs,"config.R"), echo=TRUE)


```


# Overview

The code in this replication package ....

# Data Availability and Provenance Statements

All data are public, and can be redistributed. The BEA data...

## Statement about Rights

- [x] I certify that the author(s) of the manuscript have legitimate access to and permission to use the data used in this manuscript. 
- [x] I certify that the author(s) of the manuscript have documented permission to redistribute/publish the data contained within this replication package. Appropriate permission are documented in the [LICENSE.txt](LICENSE.txt) file.


## License for Data

- BEA data is in the public domain, and can be redistributed without restriction.

All derivative data contained herein, if not otherwise encumbered, is available under a [CC-BY-NC-4.0](https://creativecommons.org/licenses/by-nc/4.0/legalcode) license. Usage by commercial entities is permitted, reselling the data is not.


## Summary of Availability

- [x] All data **are** publicly available.
- [ ] Some data **cannot be made** publicly available.
- [ ] **No data can be made** publicly available.



## Details on each Data Source

### BEA data

The data were scraped from the BEA website (`r bea.papers.html`).


# Computational requirements


## Software Requirements

- [x] The replication package contains one or more programs to install all dependencies and set up the necessary directory structure. 

- `r version$version.string` on `r version$system`


### Software citations

Skipped for today.

## Controlled Randomness



- [ ] Random seed is set at line _____ of program ______
- [x] No Pseudo random generator is used in the analysis described here.

Note that re-scraping the data (turned off by default) **may** generate different data.

## Memory, Runtime, Storage Requirements

### Summary

Approximate time needed to reproduce the analyses on a standard (CURRENT YEAR) desktop machine (when not running API queries):

- [ ] <10 minutes
- [ ] 10-60 minutes
- [ ] 1-2 hours
- [ ] 2-8 hours
- [ ] 8-24 hours
- [ ] 1-3 days
- [ ] 3-14 days
- [ ] > 14 days


Approximate storage space needed:

- [ ] < 25 MBytes
- [ ] 25 MB - 250 MB
- [ ] 250 MB - 2 GB
- [ ] 2 GB - 25 GB
- [ ] 25 GB - 250 GB
- [ ] > 250 GB

- [ ] Not feasible to run on a desktop machine, as described below.

### Details

The code was last run on (this should be parsed from the OS info)

- OS: Linux
- Processor:  AMD Ryzen 9 3900X 12-Core Processor, 24 cores
- Memory available: 31GB memory
- `r version$version.string` on `r version$system`


# Description of programs/code

Each numbered R program can be run independently, in the sequence implied by the numbering scheme. 
A convenience bash main script (`run.sh`) to run all programs is provided in the root of the project, and will run all data cleaning and analysis programs.

Internet access is required to run the programs, 

- when re-running scraping.

## Running the code

### Obtain the data

```{r}
source(file.path(programs,"01_download_data.R"),echo=TRUE)
```

### Prepare the analysis


```{r}
source(file.path(programs,"02_analyze_data.R"),echo=TRUE)
```

### Show table

```{r,results='asis'}
knitr::kable(output_table)
```

### Create output


```{r}
source(file.path(programs,"03_display_results.R"),echo=TRUE)
```


##  License for Code


The code (all files ending in `.R`, `.Rmd`, and `.sh`) is licensed under a BSD license. See [LICENSE.txt](LICENSE.txt) for details.

# Instructions to Replicators

- in the "Terminal" (of the RStudio app), run `bash ./run.sh`

Alternative ways to run this (these were not tested):

- optionally, before running project code, run `Rscript -e "renv::init()"` (on Windows, `Rscript.exe -e "renv::init()"` ) to isolate the project libraries from your system (assumes `renv` is installed, see [renv](https://rstudio.github.io/renv/articles/renv.html)).
- Using the same R version as described above, run each program individually as desired, in the order indicated above.

## Details

This should contain a list of programs and what they do.


# List of tables and programs


The provided code reproduces:

- [x] All numbers provided in text in the paper
- [x] All tables and figures in the paper
- [ ] Selected tables and figures in the paper, as explained and justified below.

---

# Acknowledgements

This README based on the template created by @template-readme. 

# References


<div id="refs"></div>

#  Appendix {-} 

## Appendix: System and package info


```{r sysinfo,eval=TRUE,echo=FALSE}
# we don't want to capture what the Rmarkdown session is running, but rather, what the computational session is running
if (! file.exists(file.path(programs,"99_zz_info.txt"))) {
system("cd programs && R CMD BATCH 99_zz_info.R")
}
```

```{r includetext,echo=FALSE,eval=TRUE}
cat(readLines(file.path(programs,"99_zz_info.txt")), sep = '\n')

```
